Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-17 manuscript/manuscript.tex
Added single figure for linear density results. Improved density-based discret figure.

@@

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{figures/linear-D.pdf}
\caption{
    Differences between the gravity fields generated by the numerical 
    model and the analytical solution for (a) a thin spherical shell of 
    1km of thickness and (b) a thick spherical shell of 35km of thickness,
    both with the linear density defined on equation 
    \ref{eq:density-linear}.
    The computations were performed on the four grids described in 
    Table \ref{tab:grids}, for different values of the distance-size 
    ratio $D$ and without applying the density-based discretization 
    algorithm.
    If the difference is less than 0.1\%, we consider that the model 
    has achieved an acceptable accuracy for the corresponding value of 
    $D$.
    }
\label{fig:D-linear}
\end{figure*}

@@

\todo[inline, color=red]{Text bellow is old}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
